---
title: "Data-Exploration"
author: "François Delavy"
date: "11/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)

library(tidyverse)

SDG_raw <- rio::import(file = "../sdg_hackathon_data.csv")

```


```{r}
glimpse(SDG_raw)
SDG_raw %>% count(system)
```

## Data Processing

Let's first not care about _system_ and _hits_, only about _svg_. We then just count if a project abstract contain any SDG according to any method/system.  

We remove the "ontology" and "sdsn" systems as they are too sensitive and blurry the picture.  

We pick ths sytsem Aurora, it's clearer if only one.

```{r }
SDG <- SDG_raw %>% 
  filter(system == "aurora") %>%
  select(-system, -hits) %>%
  filter(!is.na(sdg)) %>%
  distinct() %>%
  mutate(start_month = lubridate::floor_date(start_date, "month"))

  
```

```{r}
glimpse(SDG)
```

## quick plots

```{r}
SDG %>% 
  count(sdg) %>%
  ggplot(aes(x=sdg, y=n)) +
  geom_col() + 
  coord_flip() +
  theme_minimal() +
  ggtitle("Simple count of SDGs")
  
```

```{r}
SDG %>% 
  count(sdg, start_month) %>%
  ggplot(aes(x=start_month, y=n)) +
  geom_line() + 
  theme_minimal() +
  facet_wrap(vars(sdg), ncol=4) +
  ggtitle("Monthly mention of each SDG (any system)")
  
```

## Network

1. SDGs mentioned together
2. Universities working on same themes - network of universities

### 1. SDGs mentioned together

Counting the SDGs that we mentioned in the same abstract.  

```{r, fig.width=16, fig.height=10}

library(ggraph)
library(tidygraph)

# nodes list:
nodes <- SDG %>% count(sdg, name = "weight")

# edges list:
edges <- SDG %>%
  # only what we need:
  select(project_number, sdg) %>%
  group_by(project_number) %>%
  mutate(target = paste(sdg, collapse = ';')) %>%
  # we do not need to continue working on the grouped dataframe:
  ungroup() %>%
  # then we create a new row for all the combinations observed in the data,
  # by splitting the column added above:
  separate_rows(target, sep = ';') %>%
  select(source = sdg, target = target) %>%
  # we remove references to self:
  filter(source != target) %>%
  group_by(source, target) %>%
  summarize(weight = n())
glimpse(edges)

graph <- as_tbl_graph(edges, directed = FALSE, vertices = nodes) 
# create the layout for the graph:
set.seed(100)
# lay <- ggraph::create_layout(graph, layout = "dh") %>%
#   left_join(nodes, by = c("name" = "sdg"))

net <- ggraph(graph, layout = "stress") +
  geom_edge_link(aes(width = edges$weight), color = "grey", alpha = 0.2) +
  geom_node_point(aes(color = nodes$sdg, size=nodes$weight), shape = 19, alpha = 0.8) +
  geom_node_text(aes(label = nodes$sdg), repel = TRUE, size = 5) +
  scale_edge_width_continuous(range = c(1, 10), name = "co-Mentions") + # control size
  # scale_edge_colour_continuous(
  #   low = "#ffffff",
  #   # low = "#d3d3d3",
  #   high = "#000000",
  #   space = "Lab",
  #   na.value = "grey50",
  #   guide = NULL
  # ) +
  scale_size_continuous(name = "Number of Mentions", range = c(3, 24)) +
  # scale_color_manual(name = "Category", values = HL_colors, 
  #                    labels = c("Languages", "Platforms", "Web Frameworks", 
  #                               "Other Frameworks"))+
  coord_fixed()+
  theme_graph() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 17)
        # legend.key = element_rect(size = 5)
        ) #+ 
  # guides(colour = guide_legend(override.aes = list(size=8)))

net


```

```{r, fig.width=16, fig.height=10, include=FALSE}
net <- ggraph(graph, layout = 'kk') +
  geom_edge_link(aes(width = edges$weight), color = "grey", alpha = 0.2) +
  geom_node_point(aes(color = nodes$sdg, size=nodes$weight), shape = 19, alpha = 0.8) +
  geom_node_text(aes(label = nodes$sdg), repel = TRUE, size = 5) +
  scale_edge_width_continuous(range = c(1, 10), name = "co-Mentions") + # control size
  # scale_edge_colour_continuous(
  #   low = "#ffffff",
  #   # low = "#d3d3d3",
  #   high = "#000000",
  #   space = "Lab",
  #   na.value = "grey50",
  #   guide = NULL
  # ) +
  scale_size_continuous(name = "Number of Mentions", range = c(3, 24)) +
  # scale_color_manual(name = "Category", values = HL_colors, 
  #                    labels = c("Languages", "Platforms", "Web Frameworks", 
  #                               "Other Frameworks"))+
  coord_fixed()+
  theme_graph() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 17)
        # legend.key = element_rect(size = 5)
        ) #+ 
  # guides(colour = guide_legend(override.aes = list(size=8)))

net
```


```{r, fig.width=16, fig.height=10, include=FALSE}
net <- ggraph(graph, layout = 'dh') +
  geom_edge_link(aes(width = edges$weight), color = "grey", alpha = 0.2) +
  geom_node_point(aes(color = nodes$sdg, size=nodes$weight), shape = 19, alpha = 0.8) +
  geom_node_text(aes(label = nodes$sdg), repel = TRUE, size = 5) +
  scale_edge_width_continuous(range = c(1,10), name = "co-Mentions") + # control size
  # scale_edge_colour_continuous(
  #   low = "#ffffff",
  #   # low = "#d3d3d3",
  #   high = "#000000",
  #   space = "Lab",
  #   na.value = "grey50",
  #   guide = NULL
  # ) +
  scale_size_continuous(name = "Number of Mentions", range = c(3, 24)) +
  # scale_color_manual(name = "Category", values = HL_colors, 
  #                    labels = c("Languages", "Platforms", "Web Frameworks", 
  #                               "Other Frameworks"))+
  coord_fixed()+
  theme_graph() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 17)
        # legend.key = element_rect(size = 5)
        ) #+ 
  # guides(colour = guide_legend(override.aes = list(size=8)))

net
```

```{r, fig.width=16, fig.height=10, include=FALSE}
net <- ggraph(graph, layout = 'fr') +
  geom_edge_link(aes(width = edges$weight), color = "grey", alpha = 0.2) +
  geom_node_point(aes(color = nodes$sdg, size=nodes$weight), shape = 19, alpha = 0.8) +
  geom_node_text(aes(label = nodes$sdg), repel = TRUE, size = 5) +
  scale_edge_width_continuous(range = c(1,10), name = "co-Mentions") + # control size
  # scale_edge_colour_continuous(
  #   low = "#ffffff",
  #   # low = "#d3d3d3",
  #   high = "#000000",
  #   space = "Lab",
  #   na.value = "grey50",
  #   guide = NULL
  # ) +
  scale_size_continuous(name = "Number of Mentions", range = c(3, 24)) +
  # scale_color_manual(name = "Category", values = HL_colors, 
  #                    labels = c("Languages", "Platforms", "Web Frameworks", 
  #                               "Other Frameworks"))+
  coord_fixed()+
  theme_graph() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 17)
        # legend.key = element_rect(size = 5)
        ) #+ 
  # guides(colour = guide_legend(override.aes = list(size=8)))

net
```

```{r, fig.width=16, fig.height=10, include=FALSE}
net <- ggraph(graph, layout = 'graphopt') +
  geom_edge_link(aes(width = edges$weight), color = "grey", alpha = 0.2) +
  geom_node_point(aes(color = nodes$sdg, size=nodes$weight), shape = 19, alpha = 0.8) +
  geom_node_text(aes(label = nodes$sdg), repel = TRUE, size = 5) +
  scale_edge_width_continuous(range = c(1,10), name = "co-Mentions") + # control size
  # scale_edge_colour_continuous(
  #   low = "#ffffff",
  #   # low = "#d3d3d3",
  #   high = "#000000",
  #   space = "Lab",
  #   na.value = "grey50",
  #   guide = NULL
  # ) +
  scale_size_continuous(name = "Number of Mentions", range = c(3, 24)) +
  # scale_color_manual(name = "Category", values = HL_colors, 
  #                    labels = c("Languages", "Platforms", "Web Frameworks", 
  #                               "Other Frameworks"))+
  coord_fixed()+
  theme_graph() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 17)
        # legend.key = element_rect(size = 5)
        ) #+ 
  # guides(colour = guide_legend(override.aes = list(size=8)))

net
```


### 2. Uni

Let's try with a small SDG first: SDG-06

--- NO TIME !!! ---


```{r}

SDG_06 <- SDG %>% filter(sdg == "SDG-06")

# nodes list:



```


## Treemaps
 
We use the same data (edge list) as for the networks

```{r, fig.width=16, fig.height = 16, fig.align='center'}

library(treemapify)

SDGs_names_and_colors <- rio::import("SDGs_names_and_colors.csv")

dat <- edges %>% left_join(SDGs_names_and_colors, by = c("target" = "sdg")) %>%
  select(source, target, target_name = name, target_color = color, weight) %>%
  left_join(SDGs_names_and_colors, by = c("source" = "sdg")) %>%
  select(source, source_name = name, source_color = color, target, target_name, target_color, weight)


abstract <- dat %>%
  ggplot(aes(area = weight, fill = target_color)) +#, label = target)) +
  facet_wrap(vars(source)) +
  geom_treemap() + 
  scale_fill_identity() +
  # geom_treemap_text(grow=FALSE) +
  theme(
    legend.position = "none",
    aspect.ratio = 1,
    strip.text.x = element_text(size = 18)) +
  theme_minimal()

abstract


ggsave(file="abstract_art.svg", plot=abstract, width=10, height=10)
ggsave(file="abstract_art_larger.svg", plot=abstract, width=20, height=20)

ggsave(file="abstract_art_labels.svg", plot=abstract, width=20, height=20)


```

```{r, fig.width=4, fig.height=16, fig.align='center'}
abstract_1 <- dat %>%
  ggplot(aes(area = weight, fill = target_color, label = target)) +
  geom_treemap() + 
  facet_wrap(vars(source_name), ncol = 1) +
  scale_fill_identity() +
  # geom_treemap_text() +
  theme_minimal() +
  theme(
    legend.position = "none",
    aspect.ratio = 1,
    strip.text.x = element_text(size = 6)) 
abstract_1

ggsave(file="abstract_art_vertical.svg", plot=abstract_1, width=2, height=20)

```

```{r, fig.width=16, fig.height=3, fig.align='center'}
abstract_2 <- dat %>%
  ggplot(aes(area = weight, fill = target_color, label = target)) +
  geom_treemap() + 
  facet_wrap(vars(source_name), ncol = 17) +
  scale_fill_identity() +
  # geom_treemap_text() +
  theme_minimal() +
  theme(
    legend.position = "none",
    aspect.ratio = 1,
    strip.text.x = element_text(size = 6)) 
abstract_2

ggsave(file="abstract_art_horizontal.svg", plot=abstract_2, width=20, height=2)

```


```{r, fig.width=12, fig.height=12, fig.align='center'}
dat %>%
  ggplot(aes(area = weight, fill = target_color, label = target)) +
  geom_treemap() + 
  facet_wrap(vars(source_name)) +
  scale_fill_identity() +
  geom_treemap_text() +
  theme_minimal() +
  theme(
    legend.position = "none",
    aspect.ratio = 1,
    strip.text.x = element_text(size = 18)) 
```


```{r}
rio::export(dat, "dataset_for_treemaps.csv")
```








